---
title: "Vignette: `get_series_obs` Function"
author: "Stephanie Langeland"
date: "2017-12-11"
output: 
  html_document:
      keep_md: true
vignette: >
  %\VignetteIndexEntry{get_series_obs Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

__Package:__ `EconFiData`

__Purpose:__ Obtain Data Using a FRED API Call

__Description:__ This function uses a FRED API key to obtain economic and financial
data from https://research.stlouisfed.org/docs/api/fred/series_observations.html.
There are other packages that have functions that can also obtain these data.
This function was included in this package for completeness purposes so 
another user can re-perform this project.  

Load necessary packages:

```{r, mesage = FALSE, warning = FALSE}
library(httr)
library(jsonlite)
library(EconFiData)
```

Example 1:

  * `DFEDTAR` is the ID number for the Federal Funds Target Rate (details: https://fred.stlouisfed.org/series/DFEDTAR)
  
  * My FRED API key is saved in my `Renviron` file "FRED_API".  Users can sign
  up for a FRED API key here: https://research.stlouisfed.org/docs/api/api_key.html
  
  * More information about the frequencies available are here:
  https://research.stlouisfed.org/docs/api/fred/series_observations.html#frequency

Obtain data:

```{r}
setwd("/Users/StephanieLangeland/Desktop/")

target_data <- get_series_obs(series_id = "DFEDTAR", 
                              observation_start = "1995-01-01",
                              observation_end = "2008-12-15", 
                              user_api = Sys.getenv("FRED_API"), 
                              frequency = "d", 
                              name_rds = "Federal_Funds_Target_Rate.rds"
                              )
```

Clean data:

```{r}
head(target_data)

str(target_data)

target_data_df <- as.data.frame(target_data$observations)

View(target_data_df)

colnames(target_data_df)[4] <- "Federal_Funds_Target_Rate"

target_data_df <- target_data_df[ c("date",
                                    "Federal_Funds_Target_Rate")]

head(target_data_df)
```

