File-Name:  EDA_v6

Version: 6

Date: 03/17/17 - 04/11/17

Author: Stephanie Langeland 

Purpose: Analyze the data: final output for the project 

Input Files: "master.csv"

Output Files: None yet

Data Output: none  

Previous files: EDA_v5

Dependencies: EDA_v1 - v5

Required by: Data Analysis Final Project

Status: In progress 

Machine: Personal 2011 MacBook Pro

R version 3.3.3

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Input data: 
```{r}
rm(list = ls(all = TRUE))   # cleans everything in the workspace

master <- read.csv("/Users/StephanieLangeland/Desktop/Columbia/Data Analysis/Final Project/Cleaned data/master.csv")

master <- master[ , -1] # column X is the row number - remove that column 
```

# Split the data:
```{r}
set.seed(1234) # for reproducibility
train <- sample(nrow(master), 7836) # split the `master` data in half

## Training and testing data for all regions:
training <- master[train,] # training data
testing <- master[-train, ] # testing data

## Subset the training and testing data for each region:
training1 <- training[which(training$state_region == 1), ]
testing1 <- testing[which(testing$state_region == 1), ]

training2 <- training[which(training$state_region == 2), ]
testing2 <- testing[which(testing$state_region == 2), ]

training3 <- training[which(training$state_region == 3), ]
testing3 <- testing[which(testing$state_region == 3), ]

training4 <- training[which(training$state_region == 4), ]
testing4 <- testing[which(testing$state_region == 4), ]

training5 <- training[which(training$state_region == 5), ]
testing5 <- testing[which(testing$state_region == 5), ]

training6 <- training[which(training$state_region == 6), ]
testing6 <- testing[which(testing$state_region == 6), ]

training7 <- training[which(training$state_region == 7), ]
testing7 <- testing[which(testing$state_region == 7), ]

training8 <- training[which(training$state_region == 8), ]
testing8 <- testing[which(testing$state_region == 8), ]

training9 <- training[which(training$state_region == 9), ]
testing9 <- testing[which(testing$state_region == 9), ]
```

# Data Visualizations:
```{r}
##:::::::::::::::: Plot of the `hpa_comp_mean_direction` distribution:
sum(master$hpa_comp_mean_direction == 0)
sum(master$hpa_comp_mean_direction == 1)
summary(is.na(master$hpa_comp_mean_direction))

thing2 <- matrix(c(0, 1, "NA", 
                   8086, 7586, 0),
                 byrow = FALSE,
                 ncol = 2, 
                 nrow = 3)
thing2 <- as.data.frame(thing2)

library(ggplot2)
ggplot(data = thing2, aes(x = V1, y = V2, fill = V2)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = V2), vjust = 0, colour = "black") +
  scale_x_discrete(breaks = c(0, 1, "NA"),
                      labels = c("0 = Decrease in the HPA", 
                                "1 = Increase in the HPA",
                                "NA = Missing Values")) +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 45, hjust = 1),
        axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        axis.text.y = element_blank()) +
  ggtitle("Distribution of the Mean of HPA Data\n(hpa_mean_direction Variable)")



##:::::::::::::::: Plot of the `hpa_comp_med_direction` distribution:
sum(master$hpa_comp_med_direction == 0)
sum(master$hpa_comp_med_direction == 1)
summary(is.na(master$hpa_comp_med_direction))

thing3 <- matrix(c(0, 1, "NA",
                   8676, 6996, 0),
                 byrow = FALSE,
                 ncol = 2, 
                 nrow = 3)
thing3 <- as.data.frame(thing3)

ggplot(data = thing3, aes(x = V1, y = V2, fill = V2)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = V2), vjust = 0, colour = "black") +
  scale_x_discrete(breaks = c(0, 1, "NA"),
                      labels = c("0 = Decrease in the HPA", 
                                "1 = Increase in the HPA",
                                "NA = Missing Values")) +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 45, hjust = 1),
        axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        axis.text.y = element_blank()) +
  ggtitle("Distribution of the Median of HPA Data\n(hpa_med_direction Variable)")



##:::::::::::::::: Plot of the `H1` distribution:
sum(master$H1 == 0, na.rm = TRUE)
sum(master$H1 == 1, na.rm = TRUE)
sum(master$H1 == 2, na.rm = TRUE)
sum(master$H1 == 3, na.rm = TRUE)
sum(master$H1 == 4, na.rm = TRUE)
summary(is.na(master$H1))

thing5 <- matrix(c(0, 1, 2, 3, 4, "NA",
                   2080, 
                   3697, 
                   2855, 
                   0, 
                   506,
                   6534),
                 byrow = FALSE,
                 ncol = 2, 
                 nrow = 6)
thing5 <- as.data.frame(thing5)

ggplot(data = thing5, aes(x = V1, y = V2, fill = V2, na.rm = FALSE)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = V2), vjust = 0, colour = "black") +
  scale_x_discrete(breaks = c(0, 1, 2, 3, 4, "NA"),
                     labels = c("Lower Value",
                                "Higher Value",
                                "Refused",
                                "Stayed About the Same",
                                " \"Don't know\"",
                                "NA = Missing Values")) +
  xlab("Responses") +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 45, hjust = 1),
        axis.title.y = element_blank(),
        axis.text.y = element_blank()) +
  ggtitle("Compared to five years ago (since 2008) or compared to 12 months ago,\ndo you think the value of your home today is higher, lower or stayed the same?\n(H1 Variable)")

##^ heavy skew (nearly 3x as many "1" cases compared to "0 cases") and many people refused (= 2) to answer, skweing the data even more.



##:::::::::::::::: Plot of the `H4` distribution:
sum(master$H4 == 0, na.rm = TRUE)
sum(master$H4 == 1, na.rm = TRUE)
sum(master$H4 == 2, na.rm = TRUE)
sum(master$H4 == 3, na.rm = TRUE)
sum(master$H4 == 4, na.rm = TRUE)
summary(is.na(master$H4))

thing6 <- matrix(c(0, 1, 2, 3, 4, "NA",
                   757, 
                   3932, 
                   0, 
                   4134, 
                   1176,
                   5673),
                 byrow = FALSE,
                 ncol = 2, 
                 nrow = 6)
thing6 <- as.data.frame(thing6)

ggplot(data = thing6, aes(x = V1, y = V2, fill = V2)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = V2), vjust = 0, colour = "black") +
  scale_x_discrete(breaks = c(0, 1, 2, 3, 4, "NA"),
                     labels = c("Lower Value",
                                "Higher Value",
                                "Refused",
                                "Stay About the Same",
                                " \"Don't know\"",
                                "NA = Missing Values")) +
  xlab("Responses") +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 45, hjust = 1),
        axis.title.y = element_blank(), 
        axis.text.y = element_blank()) +
  ggtitle("In the next 12 months, how much, if at all, do you think that home\nprices in your neighborhood will change? (H4 Variable)")
## ^some skew in that there are about 1/3 less "0" cases compared to "1" cases; heavy skew due to respondents staying home values will stay ~ the same (= 3).



##:::::::::::::::: Plot of the `state_region` distribution:
sum(master$state_region == 1)
sum(master$state_region == 2)
sum(master$state_region == 3)
sum(master$state_region == 4)
sum(master$state_region == 5)
sum(master$state_region == 6)
sum(master$state_region == 7)
sum(master$state_region == 8)
sum(master$state_region == 9)

thing4 <- matrix(c(1, 2, 3, 4, 5, 6, 7, 8, 9,
                   745, 
                   2118, 
                   2519, 
                   1266, 
                   3093, 
                   847,
                   1588,
                   1164,
                   2332),
                 byrow = FALSE,
                 ncol = 2, 
                 nrow = 9)
thing4 <- as.data.frame(thing4)

ggplot(data = thing4, aes(x = V1, y = V2, fill = V2)) +
  geom_bar(stat = "identity") +
  ggtitle("Distribution of Data by Region") +
  xlab("Region") +
  ylab("Count") +
  geom_text(aes(label = V2), vjust = 0, colour = "black") +
  scale_x_continuous(breaks = c(1, 2, 3, 4, 5, 6, 7, 8, 9),
                     labels = c("New England",
                                "Mid-Atlantic",
                                "East-North Central",
                                "West-North Central",
                                "South Atlantic",
                                "East-South Central",
                                "West-South Central",
                                "Mountain",
                                "Pacific")) +
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 45, hjust = 1))



##:::::::::::::::: Summary Statistics of the Data:
library(stargazer)
stargazer(master, type = "text")

##:::::::::::::::: Plots to verify that the training and testing sets have the same skew:
hist(training$state_region)
hist(testing$state_region) ## skewed the SAME way btwn training and testing data sets - good

hist(training$hpa_comp_mean_direction) ## no skew - good
hist(testing$hpa_comp_mean_direction) ## no skew - good 

hist(training$H4) 
hist(testing$H4) ## skewed the SAME way btwn training and testing data sets 

hist(training$H1) 
hist(testing$H1) ## skewed the SAME way btwn training and testing data sets



##:::::::::::::::: Conditional density plots:
cdplot(as.factor(hpa_comp_med_direction) ~ H1, 
       data = master) ## HPA_median: conditional density plot of H1

cdplot(as.factor(hpa_comp_med_direction) ~ H4, 
       data = master) # HPA_median:  conditional density plot of H4


cdplot(as.factor(hpa_comp_med_direction) ~ H1, 
       data = master) ## HPA_median: conditional density plot of H1

cdplot(as.factor(hpa_comp_med_direction) ~ H4, 
       data = master) # HPA_median:  conditional density plot of H4
```

# OLS MODEL #1 (MEDIAN) for the hpa:
```{r}
##:::::::::::::::: MODEL #1 for all regions using master data - OLS:
lm_a_md_ols <- lm(hpa_comp_med_direction ~ H4 + H1,
                data = master)

plot(lm_a_md_ols)  ## diagnostic plots

library(MASS)
hist(studres(lm_a_md_ols),
     main = "Distribution of Studentized Residuals") ## The Studentized 
## residuals, like standardized residuals, are normalized to unit 
## variance, but the Studentized version is fitted ignoring the current 
## data point.


library(stargazer)
stargazer(lm_a_md_ols, type = "text") ## summary stats
summary(lm_a_md_ols)

with(master, table("Prediction" = H4, "Reference" =  hpa_comp_med_direction)) ## confusion matrix for H4
with(master, table("Prediction" = H1, "Reference" =  hpa_comp_med_direction)) ## confusion matrix for H1



##:::::::::::::::: MODEL #1 by region using training and testing data - OLS:

##:::::::::::::::: MODEL #1 for all regions using training and testing data - OLS:
lm_a_md <- lm(hpa_comp_med_direction ~ H4 + H1,
              data = training)

lm_a_md_pred <- predict(lm_a_md, 
                    newdata = testing,
                    type = "response")

library(caret)
lm_a_md_cm <- confusionMatrix(
  testing$hpa_comp_med_direction, 
  as.integer(lm_a_md_pred > 0.5))



##:::::::::::::::: MODEL #1 for region 1 using training and testing data - OLS:
lm_1_md <- lm(hpa_comp_med_direction ~ H4 + H1, 
              data = training1)

lm_1_md_pred <- predict(lm_1_md,
                        newdata = testing1,
                        type = "response")

#lm_1_md_cm <- confusionMatrix(
#  testing$hpa_comp_med_direction, 
#  as.integer(lm_1_md_pred > 0.5)) ## ERROR result

lm_1_md_cm <- table(
  testing1$hpa_comp_med_direction,
  as.integer(lm_1_md_pred > 0.5)
)



##:::::::::::::::: MODEL #1 for region 2 using training and testing data - OLS:
lm_2_md <- lm(hpa_comp_med_direction ~ H4 + H1, 
              data = training2)

lm_2_md_pred <- predict(lm_2_md,
                        newdata = testing2,
                        type = "response")

#lm_2_md_cm <- confusionMatrix(
#  testing2$hpa_comp_med_direction, 
#  as.integer(lm_2_md_pred > 0.5)) ## ERROR

lm_2_md_cm <- table(
  testing2$hpa_comp_med_direction,
  as.integer(lm_2_md_pred > 0.5)
)



##:::::::::::::::: MODEL #3 for region 1 using training and testing data - OLS:
lm_3_md <- lm(hpa_comp_med_direction ~ H4 + H1,
              data = training3)

lm_3_md_pred <- predict(lm_3_md,
                        newdata = testing3,
                        type = "response")

lm_3_md_cm <- confusionMatrix(
  testing3$hpa_comp_med_direction, 
  as.integer(lm_3_md_pred > 0.5)) 



##:::::::::::::::: MODEL #1 for region 4 using training and testing data - OLS:
lm_4_md <- lm(hpa_comp_med_direction ~ H4 + H1,
              data = training4)

lm_4_md_pred <- predict(lm_4_md,
                        newdata = testing4,
                        type = "response")

#lm_4_md_cm <- confusionMatrix(
#  testing4$hpa_comp_med_direction, 
#  as.integer(lm_4_md_pred > 0.5)) ## ERROR result 

lm_4_md_cm <- table(
  testing4$hpa_comp_med_direction,
  as.integer(lm_4_md_pred > 0.5)
)



##:::::::::::::::: MODEL #1 for region 5 using training and testing data - OLS:
lm_5_md <- lm(hpa_comp_med_direction ~ H4 + H1,
              data = training5)

lm_5_md_pred <- predict(lm_5_md,
                        newdata = testing5,
                        type = "response")

#lm_5_md_cm <- confusionMatrix(
#  testing5$hpa_comp_med_direction, 
#  as.integer(lm_5_md_pred > 0.5)) ## ERROR result

lm_5_md_cm <- table(
  testing5$hpa_comp_med_direction,
  as.integer(lm_5_md_pred > 0.5)
)



##:::::::::::::::: MODEL #1 for region 6 using training and testing data - OLS:
lm_6_md <- lm(hpa_comp_med_direction ~ H4 + H1,
              data = training6)

lm_6_md_pred <- predict(lm_6_md,
                        newdata = testing6,
                        type = "response")

lm_6_md_cm <- confusionMatrix(
  testing6$hpa_comp_med_direction, 
  as.integer(lm_6_md_pred > 0.5)) 



##:::::::::::::::: MODEL #1 for region 7 using training and testing data - OLS:
lm_7_md <- lm(hpa_comp_med_direction ~ H4 + H1,
              data = training7)

lm_7_md_pred <- predict(lm_7_md,
                        newdata = testing7,
                        type = "response")

#lm_7_md_cm <- confusionMatrix(
#  testing7$hpa_comp_med_direction, 
#  as.integer(lm_7_md_pred > 0.5)) ## ERROR result

lm_7_md_cm <- table(
  testing7$hpa_comp_med_direction,
  as.integer(lm_7_md_pred > 0.5)
)



##:::::::::::::::: MODEL #1 for region 8 using training and testing data - OLS:
lm_8_md <- lm(hpa_comp_med_direction ~ H4 + H1,
              data = training8)

lm_8_md_pred <- predict(lm_8_md,
                        newdata = testing8,
                        type = "response")

lm_8_md_cm <- confusionMatrix(
  testing8$hpa_comp_med_direction, 
  as.integer(lm_8_md_pred > 0.5)) 



##:::::::::::::::: MODEL #1 for region 9 using training and testing data - OLS:
lm_9_md <- lm(hpa_comp_med_direction ~ H4 + H1,
              data = training9)

lm_9_md_pred <- predict(lm_9_md,
                        newdata = testing9,
                        type = "response")

lm_9_md_cm <- confusionMatrix(
  testing9$hpa_comp_med_direction, 
  as.integer(lm_9_md_pred > 0.5)) 


##:::::::::::::::: SUMMARY OF THIS SECTION:

##:::::::::::::::: MODEL #1 for all regions using master data - OLS:
with(master, table("Prediction" = H4, "Reference" =  hpa_comp_med_direction)) ## confusion matrix for H4
with(master, table("Prediction" = H1, "Reference" =  hpa_comp_med_direction)) ## confusion matrix for H1

##:::::::::::::::: MODEL #1 confusion matrices for each region using training and testing data - OLS:
lm_a_md_cm   
lm_1_md_cm   
lm_2_md_cm  
lm_3_md_cm   
lm_4_md_cm   
lm_5_md_cm   
lm_6_md_cm   
lm_7_md_cm   
lm_8_md_cm   
lm_9_md_cm  
```

# LOGIT MODEL #1 (MEDIAN) for the hpa:
```{r}
##:::::::::::::::: MODEL #1 for all regions using master data - LOGIT:
lg_a_md <- glm(hpa_comp_med_direction ~ H4 + H1,
                data = master,
                family = binomial)

plot(lg_a_md)
hist(studres(lg_a_md),
     main = "Distribution of Studentized Residuals")

stargazer(lg_a_md, type = "text") 
summary(lg_a_md)

exp(coef(lg_a_md)) ## odds ratio 

predict(lg_a_md, 
        type = "response", 
        newdata = data.frame(H1 = c(0), 
                             H4 = c(0))) ## predicted probability when both Xs = 0 

predict(lg_a_md, 
        type = "response", 
        newdata = data.frame(H1 = c(1), 
                             H4 = c(1))) ## predicted probability when both Xs = 1 

predict(lg_a_md, 
        type = "response", 
        newdata = data.frame(H1 = c(2), 
                             H4 = c(2))) ## predicted probability when both Xs = 2

predict(lg_a_md, 
        type = "response", 
        newdata = data.frame(H1 = c(3), 
                             H4 = c(3))) ## predicted probability when both Xs = 3

predict(lg_a_md, 
        type = "response", 
        newdata = data.frame(H1 = c(4), 
                             H4 = c(4))) ## predicted probability when both Xs = 4

predict(lg_a_md, 
        type = "response", 
        newdata = data.frame(H1 = c(0), 
                             H4 = c(0))) ## predicted probability when H1 = 0

predict(lg_a_md, 
        type = "response", 
        newdata = data.frame(H1 = c(0), 
                             H4 = c(1))) ## predicted probability when H1 = 0

predict(lg_a_md, 
        type = "response", 
        newdata = data.frame(H1 = c(0), 
                             H4 = c(2))) ## predicted probability when H1 = 0

predict(lg_a_md, 
        type = "response", 
        newdata = data.frame(H1 = c(0), 
                             H4 = c(3))) ## predicted probability when H1 = 0

predict(lg_a_md, 
        type = "response", 
        newdata = data.frame(H1 = c(0), 
                             H4 = c(4))) ## predicted probability when H1 = 0

predict(lg_a_md, 
        type = "response", 
        newdata = data.frame(H1 = c(0), 
                             H4 = c(0))) ## predicted probability when H4 = 0

predict(lg_a_md, 
        type = "response", 
        newdata = data.frame(H1 = c(1), 
                             H4 = c(0))) ## predicted probability when H4 = 0

predict(lg_a_md, 
        type = "response", 
        newdata = data.frame(H1 = c(2), 
                             H4 = c(0))) ## predicted probability when H4 = 0

predict(lg_a_md, 
        type = "response", 
        newdata = data.frame(H1 = c(3), 
                             H4 = c(0))) ## predicted probability when H4 = 0

predict(lg_a_md, 
        type = "response", 
        newdata = data.frame(H1 = c(4), 
                             H4 = c(0))) ## predicted probability when H4 = 0



##:::::::::::::::: MODEL #1 by region using training and testing data - LOGIT:

##:::::::::::::::: MODEL #1 for all regions using training and testing data - LOGIT:
lg_a_md <- glm(hpa_comp_med_direction ~ H4 + H1,
                  data = training, 
                  family = binomial)

lg_a_md_pred <- predict(lg_a_md, 
                    newdata = testing,
                    type = "response")

lg_a_md_cm <- confusionMatrix(
  testing$hpa_comp_med_direction, 
  as.integer(lg_a_md_pred > 0.5))



##:::::::::::::::: MODEL #1 for region 1 using training and testing data - LOGIT:
lg_1_md <- glm(hpa_comp_med_direction ~ H4 + H1, 
              data = training1, 
              family = binomial)

lg_1_md_pred <- predict(lg_1_md,
                        newdata = testing1,
                        type = "response")

#lg_1_md_cm <- confusionMatrix(
#  testing$hpa_comp_med_direction, 
#  as.integer(lg_1_md_pred > 0.5)) ## ERROR result

lg_1_md_cm <- table(
  testing1$hpa_comp_med_direction,
  as.integer(lg_1_md_pred > 0.5)
)



##:::::::::::::::: MODEL #1 for region 2 using training and testing data - LOGIT:
lg_2_md <- glm(hpa_comp_med_direction ~ H4 + H1, 
              data = training2, 
              family = binomial)

lg_2_md_pred <- predict(lg_2_md,
                        newdata = testing2,
                        type = "response")

#lg_2_md_cm <- confusionMatrix(
#  testing2$hpa_comp_med_direction, 
#  as.integer(lg_2_md_pred > 0.5)) ## ERROR

lg_2_md_cm <- table(
  testing2$hpa_comp_med_direction,
  as.integer(lg_2_md_pred > 0.5)
)



##:::::::::::::::: MODEL #3 for region 1 using training and testing data - LOGIT:
lg_3_md <- glm(hpa_comp_med_direction ~ H4 + H1,
              data = training3, 
              family = binomial)

lg_3_md_pred <- predict(lg_3_md,
                        newdata = testing3,
                        type = "response")

lg_3_md_cm <- confusionMatrix(
  testing3$hpa_comp_med_direction, 
  as.integer(lg_3_md_pred > 0.5)) 



##:::::::::::::::: MODEL #1 for region 4 using training and testing data - LOGIT:
lg_4_md <- glm(hpa_comp_med_direction ~ H4 + H1,
              data = training4, 
              family = binomial)

lg_4_md_pred <- predict(lg_4_md,
                        newdata = testing4,
                        type = "response")

#lg_4_md_cm <- confusionMatrix(
#  testing4$hpa_comp_med_direction, 
#  as.integer(lg_4_md_pred > 0.5)) ## ERROR result 

lg_4_md_cm <- table(
  testing4$hpa_comp_med_direction,
  as.integer(lg_4_md_pred > 0.5)
)



##:::::::::::::::: MODEL #1 for region 5 using training and testing data - LOGIT:
lg_5_md <- glm(hpa_comp_med_direction ~ H4 + H1,
              data = training5, 
              family = binomial)

lg_5_md_pred <- predict(lg_5_md,
                        newdata = testing5,
                        type = "response")

#lg_5_md_cm <- confusionMatrix(
#  testing5$hpa_comp_med_direction, 
#  as.integer(lg_5_md_pred > 0.5)) ## ERROR result

lg_5_md_cm <- table(
  testing5$hpa_comp_med_direction,
  as.integer(lg_5_md_pred > 0.5)
)



##:::::::::::::::: MODEL #1 for region 6 using training and testing data - LOGIT:
lg_6_md <- glm(hpa_comp_med_direction ~ H4 + H1,
              data = training6, 
              family = binomial)

lg_6_md_pred <- predict(lg_6_md,
                        newdata = testing6,
                        type = "response")

lg_6_md_cm <- confusionMatrix(
  testing6$hpa_comp_med_direction, 
  as.integer(lg_6_md_pred > 0.5)) 



##:::::::::::::::: MODEL #1 for region 7 using training and testing data - LOGIT:
lg_7_md <- glm(hpa_comp_med_direction ~ H4 + H1,
              data = training7, 
              family = binomial)

lg_7_md_pred <- predict(lg_7_md,
                        newdata = testing7,
                        type = "response")

#lg_7_md_cm <- confusionMatrix(
#  testing7$hpa_comp_med_direction, 
#  as.integer(lg_7_md_pred > 0.5)) ## ERROR result

lg_7_md_cm <- table(
  testing7$hpa_comp_med_direction,
  as.integer(lg_7_md_pred > 0.5)
)



##:::::::::::::::: MODEL #1 for region 8 using training and testing data - LOGIT:
lg_8_md <- glm(hpa_comp_med_direction ~ H4 + H1,
              data = training8, 
              family = binomial)

lg_8_md_pred <- predict(lg_8_md,
                        newdata = testing8,
                        type = "response")

lg_8_md_cm <- confusionMatrix(
  testing8$hpa_comp_med_direction, 
  as.integer(lg_8_md_pred > 0.5)) 



##:::::::::::::::: MODEL #1 for region 9 using training and testing data - LOGIT:
lg_9_md <- glm(hpa_comp_med_direction ~ H4 + H1,
              data = training9, 
              family = binomial)

lg_9_md_pred <- predict(lg_9_md,
                        newdata = testing9,
                        type = "response")

lg_9_md_cm <- confusionMatrix(
  testing9$hpa_comp_med_direction, 
  as.integer(lg_9_md_pred > 0.5)) 



##:::::::::::::::: MODEL #1 confusion matrices for each region using training and testing data - LOGIT:
lg_a_md_cm
lg_1_md_cm   
lg_2_md_cm  
lg_3_md_cm   
lg_4_md_cm   
lg_5_md_cm   
lg_6_md_cm   
lg_7_md_cm   
lg_8_md_cm   
lg_9_md_cm  
```

# OLS MODEL 2 (MEAN) for the hpa:
```{r}
##:::::::::::::::: MODEL #2 for all regions using master data - OLS:
lm_a_mn_ols <- lm(hpa_comp_mean_direction ~ H4 + H1,
                data = master)

plot(lm_a_mn_ols)
hist(studres(lm_a_mn_ols),
     main = "Distribution of Studentized Residuals")

stargazer(lm_a_mn_ols, type = "text")
summary(lm_a_mn_ols)

with(master, table("Prediction" = H4, "Reference" =  hpa_comp_mean_direction)) ## confusion matrix for H4
with(master, table("Prediction" = H1, "Reference" =  hpa_comp_mean_direction)) ## confusion matrix for H1



##:::::::::::::::: MODEL #2 by region using training and testing data - OLS:

##:::::::::::::::: MODEL #2 for all regions using training and testing data - OLS:
lm_a_mn <- lm(hpa_comp_mean_direction ~ H4 + H1,
          data = training)

lm_a_mn_pred <- predict(lm_a_mn, 
                    newdata = testing,
                    type = "response")

lm_a_mn_cm <- confusionMatrix(
  testing$hpa_comp_mean_direction, 
  as.integer(lm_a_mn_pred > 0.5))
 


##:::::::::::::::: MODEL #2 for region 1 using training and testing data - OLS:
lm_1_mn <- lm(hpa_comp_mean_direction ~ H4 + H1,
              data = training1)

lm_1_mn_pred <- predict(lm_1_mn,
                        newdata = testing1,
                        type = "response")

#lm_1_mn_cm <- confusionMatrix(
#  testing1$hpa_comp_mean_direction, 
#  as.integer(lm_1_mn_pred > 0.5)) ## ERROR result

lm_1_mn_cm <- table(
  testing1$hpa_comp_mean_direction,
  as.integer(lm_1_mn_pred > 0.5)
)



##:::::::::::::::: MODEL #2 for region 2 using training and testing data - OLS:
lm_2_mn <- lm(hpa_comp_mean_direction ~ H4 + H1,
              data = training2)

lm_2_mn_pred <- predict(lm_2_mn,
                        newdata = testing2,
                        type = "response")

#lm_2_mn_cm <- confusionMatrix(
#  testing2$hpa_comp_mean_direction, 
#  as.integer(lm_2_mn_pred > 0.5)) ## ERROR result 

lm_2_mn_cm <- table(
  testing2$hpa_comp_mean_direction,
  as.integer(lm_2_mn_pred > 0.5)
)



##:::::::::::::::: MODEL #2 for region 3 using training and testing data - OLS:
lm_3_mn <- lm(hpa_comp_mean_direction ~ H4 + H1,
              data = training3)

lm_3_mn_pred <- predict(lm_3_mn,
                        newdata = testing3,
                        type = "response")

lm_3_mn_cm <- confusionMatrix(
  testing3$hpa_comp_mean_direction, 
  as.integer(lm_3_mn_pred > 0.5)) 



##:::::::::::::::: MODEL #2 for region 4 using training and testing data - OLS:
lm_4_mn <- lm(hpa_comp_mean_direction ~ H4 + H1,
              data = training4)

lm_4_mn_pred <- predict(lm_4_mn,
                        newdata = testing4,
                        type = "response")

#lm_4_mn_cm <- confusionMatrix(
#  testing4$hpa_comp_mean_direction, 
#  as.integer(lm_4_mn_pred > 0.5)) ## ERROR result

lm_4_mn_cm <- table(
  testing4$hpa_comp_mean_direction,
  as.integer(lm_4_mn_pred > 0.5)
  )    



##:::::::::::::::: MODEL #2 for region 5 using training and testing data - OLS:
lm_5_mn <- lm(hpa_comp_mean_direction ~ H4 + H1,
              data = training5)

lm_5_mn_pred <- predict(lm_5_mn,
                        newdata = testing5,
                        type = "response")

#lm_5_mn_cm <- confusionMatrix(
#  testing5$hpa_comp_mean_direction, 
#  as.integer(lm_5_mn_pred > 0.5)) ## ERROR result

lm_5_mn_cm <- table(
  testing5$hpa_comp_mean_direction,
  as.integer(lm_5_mn_pred > 0.5)
)



##:::::::::::::::: MODEL #2 for region 6 using training and testing data - OLS:
lm_6_mn <- lm(hpa_comp_mean_direction ~ H4 + H1,
              data = training6)

lm_6_mn_pred <- predict(lm_6_mn,
                        newdata = testing6,
                        type = "response")

lm_6_mn_cm <- confusionMatrix(
  testing6$hpa_comp_mean_direction, 
  as.integer(lm_6_mn_pred > 0.5)) 



##:::::::::::::::: MODEL #2 for region 7 using training and testing data - OLS:
lm_7_mn <- lm(hpa_comp_mean_direction ~ H4 + H1,
              data = training7)

lm_7_mn_pred <- predict(lm_7_mn,
                        newdata = testing7,
                        type = "response")

#lm_7_mn_cm <- confusionMatrix(
#  testing7$hpa_comp_mean_direction, 
#  as.integer(lm_7_mn_pred > 0.5)) ## ERROR result

lm_7_mn_cm <- table(
  testing7$hpa_comp_mean_direction,
  as.integer(lm_7_mn_pred > 0.5)
  )     



##:::::::::::::::: MODEL #2 for region 8 using training and testing data - OLS:
lm_8_mn <- lm(hpa_comp_mean_direction ~ H4 + H1,
              data = training8)

lm_8_mn_pred <- predict(lm_8_mn,
                        newdata = testing8,
                        type = "response")

lm_8_mn_cm <- confusionMatrix(
  testing8$hpa_comp_mean_direction, 
  as.integer(lm_8_mn_pred > 0.5)) 
 


##:::::::::::::::: MODEL #2 for region 9 using training and testing data - OLS:
lm_9_mn <- lm(hpa_comp_mean_direction ~ H4 + H1,
              data = training9)

lm_9_mn_pred <- predict(lm_9_mn,
                        newdata = testing9,
                        type = "response")

lm_9_mn_cm <- confusionMatrix(
  testing9$hpa_comp_mean_direction, 
  as.integer(lm_9_mn_pred > 0.5)) 



##:::::::::::::::: SUMMARY OF THIS SECTION:

##:::::::::::::::: MODEL #2 for all regions using master data - OLS:
with(master, table("Prediction" = H4, "Reference" =  hpa_comp_mean_direction)) ## confusion matrix for H4
with(master, table("Prediction" = H1, "Reference" =  hpa_comp_mean_direction)) ## confusion matrix for H1

##:::::::::::::::: MODEL #2 confusion matrices for each region using training and testing data - OLS:
lm_a_mn_cm   
lm_1_mn_cm   
lm_2_mn_cm    
lm_3_mn_cm   
lm_4_mn_cm  
lm_5_mn_cm   
lm_6_mn_cm   
lm_7_mn_cm   
lm_8_mn_cm   
lm_9_mn_cm   
```

# LOGIT MODEL 2 (MEAN) for the hpa:
```{r}
##:::::::::::::::: MODEL #2 for all regions using master data - LOGIT:
lg_a_mn <- glm(hpa_comp_mean_direction ~ H4 + H1,
                data = master, 
                family = binomial)

plot(lg_a_mn)
hist(studres(lg_a_mn),
     main = "Distribution of Studentized Residuals")

stargazer(lg_a_mn, type = "text") 
summary(lg_a_mn)

exp(coef(lg_a_mn))

predict(lg_a_mn, 
        type = "response", 
        newdata = data.frame(H1 = c(0), 
                             H4 = c(0))) ## predicted probability when both Xs = 0

predict(lg_a_mn, 
        type = "response", 
        newdata = data.frame(H1 = c(1), 
                             H4 = c(1))) ## predicted probability when both Xs = 1

predict(lg_a_mn, 
        type = "response", 
        newdata = data.frame(H1 = c(2), 
                             H4 = c(2))) ## predicted probability when both Xs = 2

predict(lg_a_mn, 
        type = "response", 
        newdata = data.frame(H1 = c(3), 
                             H4 = c(3))) ## predicted probability when both Xs = 3

predict(lg_a_mn, 
        type = "response", 
        newdata = data.frame(H1 = c(4), 
                             H4 = c(4))) ## predicted probability when both Xs = 4

predict(lg_a_mn, 
        type = "response", 
        newdata = data.frame(H1 = c(0), 
                             H4 = c(0))) ## predicted probability when H1 = 0

predict(lg_a_mn, 
        type = "response", 
        newdata = data.frame(H1 = c(0), 
                             H4 = c(1))) ## predicted probability when H1 = 0

predict(lg_a_mn, 
        type = "response", 
        newdata = data.frame(H1 = c(0), 
                             H4 = c(2))) ## predicted probability when H1 = 0

predict(lg_a_mn, 
        type = "response", 
        newdata = data.frame(H1 = c(0), 
                             H4 = c(3))) ## predicted probability when H1 = 0

predict(lg_a_mn, 
        type = "response", 
        newdata = data.frame(H1 = c(0), 
                             H4 = c(4))) ## predicted probability when H1 = 0

predict(lg_a_mn, 
        type = "response", 
        newdata = data.frame(H1 = c(0), 
                             H4 = c(0))) ## predicted probability when H4 = 0

predict(lg_a_mn, 
        type = "response", 
        newdata = data.frame(H1 = c(1), 
                             H4 = c(0))) ## predicted probability when H4 = 0

predict(lg_a_mn, 
        type = "response", 
        newdata = data.frame(H1 = c(2), 
                             H4 = c(0))) ## predicted probability when H4 = 0

predict(lg_a_mn, 
        type = "response", 
        newdata = data.frame(H1 = c(3), 
                             H4 = c(0))) ## predicted probability when H4 = 0

predict(lg_a_mn, 
        type = "response", 
        newdata = data.frame(H1 = c(4), 
                             H4 = c(0))) ## predicted probability when H4 = 0



##:::::::::::::::: MODEL #2 by region using training and testing data - LOGIT:

##:::::::::::::::: MODEL #2 for all regions using training and testing data - LOGIT:
lg_a_mn <- glm(hpa_comp_mean_direction ~ H4 + H1,
                  data = training, 
                  family = binomial)

lg_a_mn_pred <- predict(lg_a_mn, 
                    newdata = testing,
                    type = "response")

lg_a_mn_cm <- confusionMatrix(
  testing$hpa_comp_mean_direction, 
  as.integer(lg_a_mn_pred > 0.5))



##:::::::::::::::: MODEL #2 for region 1 using training and testing data - LOGIT:
lg_1_mn <- glm(hpa_comp_mean_direction ~ H4 + H1, 
              data = training1, 
              family = binomial)

lg_1_mn_pred <- predict(lg_1_mn,
                        newdata = testing1,
                        type = "response")

#lg_1_mn_cm <- confusionMatrix(
#  testing$hpa_comp_mean_direction, 
#  as.integer(lg_1_mn_pred > 0.5)) ## ERROR result

lg_1_mn_cm <- table(
  testing1$hpa_comp_mean_direction,
  as.integer(lg_1_mn_pred > 0.5)
)



##:::::::::::::::: MODEL #2 for region 2 using training and testing data - LOGIT:
lg_2_mn <- glm(hpa_comp_mean_direction ~ H4 + H1, 
              data = training2, 
              family = binomial)

lg_2_mn_pred <- predict(lg_2_mn,
                        newdata = testing2,
                        type = "response")

#lg_2_mn_cm <- confusionMatrix(
#  testing2$hpa_comp_mean_direction, 
#  as.integer(lg_2_mn_pred > 0.5)) ## ERROR

lg_2_mn_cm <- table(
  testing2$hpa_comp_mean_direction,
  as.integer(lg_2_mn_pred > 0.5)
)



##:::::::::::::::: MODEL #3 for region 1 using training and testing data - LOGIT:
lg_3_mn <- glm(hpa_comp_mean_direction ~ H4 + H1,
              data = training3, 
              family = binomial)

lg_3_mn_pred <- predict(lg_3_mn,
                        newdata = testing3,
                        type = "response")

lg_3_mn_cm <- confusionMatrix(
  testing3$hpa_comp_mean_direction, 
  as.integer(lg_3_mn_pred > 0.5)) 



##:::::::::::::::: MODEL #2 for region 4 using training and testing data - LOGIT:
lg_4_mn <- glm(hpa_comp_mean_direction ~ H4 + H1,
              data = training4, 
              family = binomial)

lg_4_mn_pred <- predict(lg_4_mn,
                        newdata = testing4,
                        type = "response")

#lg_4_mn_cm <- confusionMatrix(
#  testing4$hpa_comp_mean_direction, 
#  as.integer(lg_4_mn_pred > 0.5)) ## ERROR result 

lg_4_mn_cm <- table(
  testing4$hpa_comp_mean_direction,
  as.integer(lg_4_mn_pred > 0.5)
)



##:::::::::::::::: MODEL #2 for region 5 using training and testing data - LOGIT:
lg_5_mn <- glm(hpa_comp_mean_direction ~ H4 + H1,
              data = training5, 
              family = binomial)

lg_5_mn_pred <- predict(lg_5_mn,
                        newdata = testing5,
                        type = "response")

#lg_5_mn_cm <- confusionMatrix(
#  testing5$hpa_comp_mean_direction, 
#  as.integer(lg_5_mn_pred > 0.5)) ## ERROR result

lg_5_mn_cm <- table(
  testing5$hpa_comp_mean_direction,
  as.integer(lg_5_mn_pred > 0.5)
)



##:::::::::::::::: MODEL #2 for region 6 using training and testing data - LOGIT:
lg_6_mn <- glm(hpa_comp_mean_direction ~ H4 + H1,
              data = training6, 
              family = binomial)

lg_6_mn_pred <- predict(lg_6_mn,
                        newdata = testing6,
                        type = "response")

lg_6_mn_cm <- confusionMatrix(
  testing6$hpa_comp_mean_direction, 
  as.integer(lg_6_mn_pred > 0.5)) 



##:::::::::::::::: MODEL #2 for region 7 using training and testing data - LOGIT:
lg_7_mn <- glm(hpa_comp_mean_direction ~ H4 + H1,
              data = training7, 
              family = binomial)

lg_7_mn_pred <- predict(lg_7_mn,
                        newdata = testing7,
                        type = "response")

#lg_7_mn_cm <- confusionMatrix(
#  testing7$hpa_comp_mean_direction, 
#  as.integer(lg_7_mn_pred > 0.5)) ## ERROR result

lg_7_mn_cm <- table(
  testing7$hpa_comp_mean_direction,
  as.integer(lg_7_mn_pred > 0.5)
)



##:::::::::::::::: MODEL #2 for region 8 using training and testing data - LOGIT:
lg_8_mn <- glm(hpa_comp_mean_direction ~ H4 + H1,
              data = training8, 
              family = binomial)

lg_8_mn_pred <- predict(lg_8_mn,
                        newdata = testing8,
                        type = "response")

lg_8_mn_cm <- confusionMatrix(
  testing8$hpa_comp_mean_direction, 
  as.integer(lg_8_mn_pred > 0.5)) 



##:::::::::::::::: MODEL #2 for region 9 using training and testing data - LOGIT:
lg_9_mn <- glm(hpa_comp_mean_direction ~ H4 + H1,
              data = training9, 
              family = binomial)

lg_9_mn_pred <- predict(lg_9_mn,
                        newdata = testing9,
                        type = "response")

lg_9_mn_cm <- confusionMatrix(
  testing9$hpa_comp_mean_direction, 
  as.integer(lg_9_mn_pred > 0.5)) 



##:::::::::::::::: MODEL #2 confusion matrices for each region using training and testing data - LOGIT:
lg_a_mn_cm
lg_1_mn_cm   
lg_2_mn_cm  
lg_3_mn_cm   
lg_4_mn_cm   
lg_5_mn_cm   
lg_6_mn_cm   
lg_7_mn_cm   
lg_8_mn_cm   
lg_9_mn_cm  
```
