File-Name:  EDA_v5

Version: 5

Date: 03/17/17 

Author: Stephanie Langeland 

Purpose: Create a master dataset. 

Input Files: "shed_final.csv" and "corelogic_final.csv"

Output Files: master.csv

Data Output: none 

Previous files: EDA_v4

Dependencies: EDA_v1 - v4

Required by: Data Analysis Final Project

Status: In progress 

Machine: Personal 2011 MacBook Pro

R version 3.3.3

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Part 1:  Bring in relevant data from `corelogic_final` into `shed_final` to create a `master` dataset: 

```{r}
rm(list = ls(all = TRUE))   # cleans everything in the workspace

# SHED:
shed_final <- read.csv("/Users/StephanieLangeland/Desktop/Columbia/Data Analysis/Final Project/Cleaned data/shed_final.csv")

# Core Logic:
corelogic_final <- read.csv("/Users/StephanieLangeland/Desktop/Columbia/Data Analysis/Final Project/Cleaned data/corelogic_final.csv")

# `master` dataset creation:

master_raw1 <- shed_final

master_raw1 <- master_raw1[ ,-1] # delete column X because it is the row number - not needed

names(master_raw1)[names(master_raw1) == "year_comp"] <- "year" # rename `year_comp` column to `year`

# the corelogic data is quarterly and the shed data is annual - will create a column that
# averages the quarters per year and another column that takes the median per year out of all
# 4 quarters:

library(dplyr)

corelogic_means_all <- group_by(corelogic_final, state_region, year) %>%
  summarize(hpi_comp_mean = mean(hpi_Comprehensive),
            hpi_fsp_mean = mean(hpi_SFP),
            hpa_comp_mean = mean(hpa_Comprehensive),
            hpa_fsp_mean = mean(hpa_SFP)
            ) # mean values for each corelogic index by state_region and year - for all years

corelogic_means_all <- as.data.frame(corelogic_means_all)

sub_2013 <- subset(corelogic_means_all, year == 2013) # subset only 2014

sub_2014 <- subset(corelogic_means_all, year == 2014) # subset only 2014

sub_2015 <- subset(corelogic_means_all, year == 2015) # subset only 2015

sub_2016 <- subset(corelogic_means_all, year == 2016) # subset only 2016

sub_13_14 <- merge(x = sub_2013, 
                   y = sub_2014,
                   all = TRUE) # merge 2013 - 2014 by columns

sub_15_16 <- merge(x = sub_2015, 
                   y = sub_2016,
                   all = TRUE) # merge 2015 - 2016 by columns

corelogic_means <- merge(x = sub_13_14, 
                         y = sub_15_16,
                         all = TRUE) # corelogic index means for 2013 - 2016

corelogic_medians_all <- group_by(corelogic_final, state_region, year) %>%
  summarize(hpi_comp_med = median(hpi_Comprehensive),
            hpi_fsp_med = median(hpi_SFP),
            hpa_comp_med = median(hpa_Comprehensive),
            hpa_sfp_med = median(hpa_SFP)
            ) # medon values for each corelogic index by state_region and year - for all years

corelogic_medians_all <- as.data.frame(corelogic_medians_all)

sub_2013m <- subset(corelogic_medians_all, year == 2013) # subset only 2014

sub_2014m <- subset(corelogic_medians_all, year == 2014) # subset only 2014

sub_2015m <- subset(corelogic_medians_all, year == 2015) # subset only 2015

sub_2016m <- subset(corelogic_medians_all, year == 2016) # subset only 2016

sub_13_14m <- merge(x = sub_2013m, 
                   y = sub_2014m,
                   all = TRUE) # merge 2013 - 2014 by columns

sub_15_16m <- merge(x = sub_2015m, 
                   y = sub_2016m,
                   all = TRUE) # merge 2015 - 2016 by columns

corelogic_medians <- merge(x = sub_13_14m, 
                         y = sub_15_16m,
                         all = TRUE) # corelogic index medians for 2013 - 2016

corelogic_subset <- merge(x = corelogic_means,
                          y = corelogic_medians) # merge `corelogic_means` and `corelogic_medians`

master <- merge(x = master_raw1, 
               y = corelogic_subset, 
               all = TRUE) # merge `corelogic_subset` and `master_raw1` by state_region and year

## Delete columns that have the exact same info - anything with FSP because that's a CCAR scenario:
colnames(master)
### 1) `hpi_comp_mean` and `hpi_fsp_mean` - delete `hpi_fsp_mean` - column 10
### 2) `hpa_comp_mean` and `hpa_fsp_mean` - delete `hpa_fsp_mean` - column 12
### 3) `hpi_comp_med` and `hpi_fsp_med`  - delete `hpi_fsp_med` - column 14
### 4) `hpa_comp_med` and `hpa_sfp_med` - delete `hpa_sfp_med` - column 16
master <- master[ , -c(10, 12, 14, 16)]

## Procedure to create the `hpa_change` variables:
### Create a unique ID# such that <year>_<state_region>:
master$new_id <- paste(master$year, master$state_region, sep = "_")

### Add the column for the following year's HPA for each observation:
master$hpa_comp_mean_year_follow <-
  ifelse(master$new_id == "2013_1", 
         subset(master$hpa_comp_mean, master$year == "2014" & master$state_region == "1"),
         ifelse(master$new_id == "2013_2", 
                subset(master$hpa_comp_mean, master$year == "2014" & master$state_region == "2"),
                ifelse(master$new_id == "2013_3", 
                       subset(master$hpa_comp_mean, master$year == "2014" & master$state_region == "3"),
                       ifelse(master$new_id == "2013_4", 
                              subset(master$hpa_comp_mean, 
                                     master$year == "2014" & master$state_region == "4"),
                              ifelse(master$new_id == "2013_5",
                                     subset(master$hpa_comp_mean, 
                                            master$year == "2014" & master$state_region == "5"),
                                     ifelse(master$new_id == "2013_6",
                                            subset(master$hpa_comp_mean, 
                                                   master$year == "2014" & master$state_region == "6"),
                                            ifelse(master$new_id == "2013_7", 
                                                   subset(master$hpa_comp_mean, 
                                                          master$year == "2014" & 
                                                            master$state_region == "7"),
                                                   ifelse(master$new_id == "2013_8",
                                                          subset(master$hpa_comp_mean, 
                                                                 master$year == "2014" & 
                                                                   master$state_region == "8"),
                                                          ifelse(master$new_id == "2013_9",
                                                                 subset(master$hpa_comp_mean, 
                                                                        master$year == "2014" &
                                                                          master$state_region == "9"),
                                                                 ifelse(master$new_id == "2014_1",
                                                                        subset(master$hpa_comp_mean,
                                                                               master$year == "2015" &
                                                                                 master$state_region == "1"),
                                                                        ifelse(master$new_id == "2014_2",
                                                                               subset(master$hpa_comp_mean,
                                                                                      master$year == "2015" &
                                                                                        master$state_region
                                                                                      == "2"),
                                                                               ifelse(
                                                                                 master$new_id == "2014_3",
                                                                                 subset(master$hpa_comp_mean,
                                                                                        master$year == "2015"
                                                                                        & master$state_region
                                                                                        == "3"),
                                                                                 ifelse(
                                                                                   master$new_id == "2014_4",
                                                                                subset(master$hpa_comp_mean,
                                                                                      master$year == "2015" &
                                                                                        master$state_region
                                                                                      == "4"),
                                                                                ifelse(master$new_id 
                                                                                       == "2014_5",
                                                                               subset(master$hpa_comp_mean,
                                                                                      master$year == "2015" &
                                                                                        master$state_region
                                                                                      == "5"),
                                                                               ifelse(master$new_id 
                                                                                      == "2014_6",
                                                                               subset(master$hpa_comp_mean,
                                                                                      master$year == "2015" &
                                                                                        master$state_region 
                                                                                      == "6"),
                                                                               ifelse(master$new_id 
                                                                                      == "2014_7",
                                                                               subset(master$hpa_comp_mean,
                                                                                      master$year == "2015" &
                                                                                        master$state_region 
                                                                                      == "7"),
                                                                               ifelse(master$new_id 
                                                                                      == "2014_8",
                                                                               subset(master$hpa_comp_mean,
                                                                                      master$year == "2015" &
                                                                                        master$state_region 
                                                                                      == "8"),
                                                                               ifelse(master$new_id 
                                                                                      == "2014_9",
                                                                               subset(master$hpa_comp_mean,
                                                                                      master$year == "2015" &
                                                                                        master$state_region 
                                                                                      == "9"),
                                                                               ifelse(master$new_id 
                                                                                      == "2015_1",
                                                                               subset(master$hpa_comp_mean,
                                                                                      master$year == "2016" &
                                                                                        master$state_region 
                                                                                      == "1"),
                                                                               ifelse(master$new_id 
                                                                                      == "2015_2",
                                                                               subset(master$hpa_comp_mean,
                                                                                      master$year == "2016" &
                                                                                        master$state_region 
                                                                                      == "2"),
                                                                               ifelse(master$new_id 
                                                                                      == "2015_3",
                                                                               subset(master$hpa_comp_mean,
                                                                                      master$year == "2016" &
                                                                                        master$state_region 
                                                                                      == "3"),
                                                                               ifelse(master$new_id 
                                                                                      == "2015_4",
                                                                               subset(master$hpa_comp_mean,
                                                                                      master$year == "2016" &
                                                                                        master$state_region 
                                                                                      == "4"),
                                                                               ifelse(master$new_id 
                                                                                      == "2015_5",
                                                                               subset(master$hpa_comp_mean,
                                                                                      master$year == "2016" &
                                                                                        master$state_region 
                                                                                      == "5"),
                                                                               ifelse(master$new_id 
                                                                                      == "2015_6",
                                                                               subset(master$hpa_comp_mean,
                                                                                      master$year == "2016" &
                                                                                        master$state_region 
                                                                                      == "6"),
                                                                               ifelse(master$new_id 
                                                                                      == "2015_7",
                                                                               subset(master$hpa_comp_mean,
                                                                                      master$year == "2016" &
                                                                                        master$state_region 
                                                                                      == "7"),
                                                                               ifelse(master$new_id 
                                                                                      == "2015_8",
                                                                               subset(master$hpa_comp_mean,
                                                                                      master$year == "2016" &
                                                                                        master$state_region 
                                                                                      == "8"),
                                                                               ifelse(master$new_id 
                                                                                      == "2015_9",
                                                                               subset(master$hpa_comp_mean,
                                                                                      master$year == "2016" &
                                                                                        master$state_region 
                                                                                      == "9"), 
                                                                               "nope")))))))))))))))))))))))))))
                                                                               
## Create the `hpa_change` variable = `hpa_comp_mean_change`:
master$hpa_comp_mean_change <- as.numeric(master$hpa_comp_mean_year_follow) - master$hpa_comp_mean

## Create the `hpa_direction` variable = `hpa_comp_mean_direction`:
master$hpa_comp_mean_direction <- ifelse(master$hpa_comp_mean_change > 0, "1", 
                                          ifelse(master$hpa_comp_mean_change < 0, "0", "nope"))

### Add the column for the following year's HPA for each observation:
master$hpa_comp_med_year_follow <-
  ifelse(master$new_id == "2013_1", 
         subset(master$hpa_comp_med, master$year == "2014" & master$state_region == "1"),
         ifelse(master$new_id == "2013_2", 
                subset(master$hpa_comp_med, master$year == "2014" & master$state_region == "2"),
                ifelse(master$new_id == "2013_3", 
                       subset(master$hpa_comp_med, master$year == "2014" & master$state_region == "3"),
                       ifelse(master$new_id == "2013_4", 
                              subset(master$hpa_comp_med, 
                                     master$year == "2014" & master$state_region == "4"),
                              ifelse(master$new_id == "2013_5",
                                     subset(master$hpa_comp_med, 
                                            master$year == "2014" & master$state_region == "5"),
                                     ifelse(master$new_id == "2013_6",
                                            subset(master$hpa_comp_med, 
                                                   master$year == "2014" & master$state_region == "6"),
                                            ifelse(master$new_id == "2013_7", 
                                                   subset(master$hpa_comp_med, 
                                                          master$year == "2014" & 
                                                            master$state_region == "7"),
                                                   ifelse(master$new_id == "2013_8",
                                                          subset(master$hpa_comp_med, 
                                                                 master$year == "2014" & 
                                                                   master$state_region == "8"),
                                                          ifelse(master$new_id == "2013_9",
                                                                 subset(master$hpa_comp_med, 
                                                                        master$year == "2014" &
                                                                          master$state_region == "9"),
                                                                 ifelse(master$new_id == "2014_1",
                                                                        subset(master$hpa_comp_med,
                                                                               master$year == "2015" &
                                                                                 master$state_region == "1"),
                                                                        ifelse(master$new_id == "2014_2",
                                                                               subset(master$hpa_comp_med,
                                                                                      master$year == "2015" &
                                                                                        master$state_region
                                                                                      == "2"),
                                                                               ifelse(
                                                                                 master$new_id == "2014_3",
                                                                                 subset(master$hpa_comp_med,
                                                                                        master$year == "2015"
                                                                                        & master$state_region
                                                                                        == "3"),
                                                                                 ifelse(
                                                                                   master$new_id == "2014_4",
                                                                                subset(master$hpa_comp_med,
                                                                                      master$year == "2015" &
                                                                                        master$state_region
                                                                                      == "4"),
                                                                                ifelse(master$new_id 
                                                                                       == "2014_5",
                                                                               subset(master$hpa_comp_med,
                                                                                      master$year == "2015" &
                                                                                        master$state_region
                                                                                      == "5"),
                                                                               ifelse(master$new_id 
                                                                                      == "2014_6",
                                                                               subset(master$hpa_comp_med,
                                                                                      master$year == "2015" &
                                                                                        master$state_region 
                                                                                      == "6"),
                                                                               ifelse(master$new_id 
                                                                                      == "2014_7",
                                                                               subset(master$hpa_comp_med,
                                                                                      master$year == "2015" &
                                                                                        master$state_region 
                                                                                      == "7"),
                                                                               ifelse(master$new_id 
                                                                                      == "2014_8",
                                                                               subset(master$hpa_comp_med,
                                                                                      master$year == "2015" &
                                                                                        master$state_region 
                                                                                      == "8"),
                                                                               ifelse(master$new_id 
                                                                                      == "2014_9",
                                                                               subset(master$hpa_comp_med,
                                                                                      master$year == "2015" &
                                                                                        master$state_region 
                                                                                      == "9"),
                                                                               ifelse(master$new_id 
                                                                                      == "2015_1",
                                                                               subset(master$hpa_comp_med,
                                                                                      master$year == "2016" &
                                                                                        master$state_region 
                                                                                      == "1"),
                                                                               ifelse(master$new_id 
                                                                                      == "2015_2",
                                                                               subset(master$hpa_comp_med,
                                                                                      master$year == "2016" &
                                                                                        master$state_region 
                                                                                      == "2"),
                                                                               ifelse(master$new_id 
                                                                                      == "2015_3",
                                                                               subset(master$hpa_comp_med,
                                                                                      master$year == "2016" &
                                                                                        master$state_region 
                                                                                      == "3"),
                                                                               ifelse(master$new_id 
                                                                                      == "2015_4",
                                                                               subset(master$hpa_comp_med,
                                                                                      master$year == "2016" &
                                                                                        master$state_region 
                                                                                      == "4"),
                                                                               ifelse(master$new_id 
                                                                                      == "2015_5",
                                                                               subset(master$hpa_comp_med,
                                                                                      master$year == "2016" &
                                                                                        master$state_region 
                                                                                      == "5"),
                                                                               ifelse(master$new_id 
                                                                                      == "2015_6",
                                                                               subset(master$hpa_comp_med,
                                                                                      master$year == "2016" &
                                                                                        master$state_region 
                                                                                      == "6"),
                                                                               ifelse(master$new_id 
                                                                                      == "2015_7",
                                                                               subset(master$hpa_comp_med,
                                                                                      master$year == "2016" &
                                                                                        master$state_region 
                                                                                      == "7"),
                                                                               ifelse(master$new_id 
                                                                                      == "2015_8",
                                                                               subset(master$hpa_comp_med,
                                                                                      master$year == "2016" &
                                                                                        master$state_region 
                                                                                      == "8"),
                                                                               ifelse(master$new_id 
                                                                                      == "2015_9",
                                                                               subset(master$hpa_comp_med,
                                                                                      master$year == "2016" &
                                                                                        master$state_region 
                                                                                      == "9"), 
                                                                               "nope")))))))))))))))))))))))))))
                                                                               
## Create the `hpa_change` variable = `hpa_comp_med_change`:
master$hpa_comp_med_change <- as.numeric(master$hpa_comp_med_year_follow) - master$hpa_comp_med

## Create the `hpa_direction` variable = `hpa_comp_med_direction`:
master$hpa_comp_med_direction <- ifelse(master$hpa_comp_med_change > 0, "1", 
                                          ifelse(master$hpa_comp_med_change < 0, "0", master$hpa_comp_med_change))

## Delete the rows where `state_region` = "CORELOGIC":
which(master$state_region == "CORELOGIC")
master <- master[-c(4135, 10032, 15675, 15685), ]

## Delete the 2016 rows because SHED data for those rows don't exist:
which(master$year == 2016)
master <- master[-c(15673:15681), ]

master.csv <- write.csv(master, file = "master.csv") # write `master` to csv file
```

