File-Name:  EDA_v4

Version: 4

Date: 03/05/17 

Author: Stephanie Langeland 

Purpose: Create a SHED dataset with only variables that I want to examine and clean the Corelogic data. 

Input Files: SHED 2013 - 2015, core logic data

Output Files: corelogic_final.csv and shed_final.csv

Data Output: shed_final.csv and corelogic_final.csv

Previous files: EDA_v3

Dependencies:  EDA_v1 - v3

Required by: Data Analysis Final Project

Status: In progress 

Machine: Personal 2011 MacBook Pro

R version 3.3.1

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Preparing/cleaning the data
```{r}
rm(list = ls(all = TRUE))   # cleans everything in the workspace

path <- "/Users/StephanieLangeland/Desktop/Columbia/Data Analysis/Final Project"

shed_data  <- "/SHED Data"
core_logic <- "/CoreLogic"

setwd(path)
getwd()
```

## Part 1:  SHED Data

```{r}
shed13 <- read.csv("/Users/StephanieLangeland/Desktop/Columbia/Data Analysis/Final Project/SHED Data/SHED_public_use_data_2013.csv")

shed14 <- read.csv("/Users/StephanieLangeland/Desktop/Columbia/Data Analysis/Final Project/SHED Data/SHED_public_use_data_2014_update (occupation industry).csv")

shed15 <- read.csv("/Users/StephanieLangeland/Desktop/Columbia/Data Analysis/Final Project/SHED Data/SHED 2015 public use.csv")

# ::::::::::::Create individual datasets for each year and format the output so 
# ::::::::::::that it is uniform in each data frame:

# Create year_comp variable = year survey was completed varaible: 
shed13$year_comp <- c("2013")
shed14$year_comp <- c("2014")
shed15$year_comp <- c("2015")

# 2013:
shed_master <- data.frame(shed13$CaseID) #create shed_master data.frame
names(shed_master)[names(shed_master) == "shed13.CaseID"] <- "CaseID" #rename CaseID column

shed_master$year_comp <- shed13$year_comp 

shed_master$H4 <- shed13$H4

shed_master$H1 <- shed13$H1

shed_master$year_buy <- shed13$H0

shed_master$MSA <- shed13$PPMSACAT

shed_master$region <- shed13$PPREG4

shed_master$state_region <- shed13$PPREG9

# 2014:
shed_master1 <- data.frame(shed14$CaseID) 
names(shed_master1)[names(shed_master1) == "shed14.CaseID"] <- "CaseID" 

shed_master1$year_comp <- shed14$year_comp 

shed_master1$H4 <- shed14$H4

shed_master1$H1 <- shed14$H1

shed_master1$year_buy <- shed14$D6

shed_master1$MSA <- shed14$ppmsacat

shed_master1$region <- shed14$ppreg4

shed_master1$state_region <- shed14$ppreg9

# 2015:
shed_master2 <- data.frame(shed15$CaseID) 
names(shed_master2)[names(shed_master2) == "shed15.CaseID"] <- "CaseID" 

shed_master2$year_comp <- shed15$year_comp 

shed_master2$H4 <- shed15$H4
summary(shed_master2$H4)
library(car)
shed_master2$H4 <- recode(shed_master2$H4, " 'Refused' = -1")
shed_master2$H4 <- recode(shed_master2$H4, " 'Go down by a lot' = 1")
shed_master2$H4 <- recode(shed_master2$H4, " 'Go down by a little' = 2")
shed_master2$H4 <- recode(shed_master2$H4, " 'Stay about the same' = 3")
shed_master2$H4 <- recode(shed_master2$H4, " 'Go up by a little' = 4")
shed_master2$H4 <- recode(shed_master2$H4, " 'Go up by a lot' = 5")
shed_master2$H4 <- recode(shed_master2$H4, " \"Don't know\" = 8")
shed_master2$H4 <- recode(shed_master2$H4, " '' = NA")

shed_master2$H1 <- shed15$H1
summary(shed_master2$H1)
shed_master2$H1 <- recode(shed_master2$H1, " 'Refused' = -1")
shed_master2$H1 <- recode(shed_master2$H1, " 'Value is a lot lower' = 1")
shed_master2$H1 <- recode(shed_master2$H1, " 'Value is a little lower' = 1")
shed_master2$H1 <- recode(shed_master2$H1, " 'Value has stayed the same' = 2")
shed_master2$H1 <- recode(shed_master2$H1, " 'Value is a little higher' = 3")
shed_master2$H1 <- recode(shed_master2$H1, " 'Value is a lot higher' = 3")
shed_master2$H1 <- recode(shed_master2$H1, " \"Don't Know\" = 8")
shed_master2$H1 <- recode(shed_master2$H1, " '' = NA")

shed_master2$year_buy <- shed15$GH2

shed_master2$MSA <- shed15$ppmsacat
summary(shed_master2$MSA)
shed_master2$MSA <- recode(shed_master2$MSA, " 'Non-Metro' = 0")
shed_master2$MSA <- recode(shed_master2$MSA, " 'Metro' = 1")

shed_master2$region <- shed15$ppreg4
summary(shed_master2$region)
shed_master2$region <- recode(shed_master2$region, " 'Northeast' = 1")
shed_master2$region <- recode(shed_master2$region, " 'Midwest' = 2")
shed_master2$region <- recode(shed_master2$region, " 'South' = 3")
shed_master2$region <- recode(shed_master2$region, " 'West' = 4")

shed_master2$state_region <- shed15$ppreg9
summary(shed_master2$state_region)
shed_master2$state_region <- recode(shed_master2$state_region, " 'New England' = 1")
shed_master2$state_region <- recode(shed_master2$state_region, " 'Mid-Atlantic' = 2")
shed_master2$state_region <- recode(shed_master2$state_region, " 'East-North Central' = 3")
shed_master2$state_region <- recode(shed_master2$state_region, " 'West-North Central' = 4")
shed_master2$state_region <- recode(shed_master2$state_region, " 'South Atlantic' = 5")
shed_master2$state_region <- recode(shed_master2$state_region, " 'East-South Central' = 6")
shed_master2$state_region <- recode(shed_master2$state_region, " 'West-South Central' = 7")
shed_master2$state_region <- recode(shed_master2$state_region, " 'Mountain' = 8")
shed_master2$state_region <- recode(shed_master2$state_region, " 'Pacific' = 9")

summary(shed_master2)

# ::::::::::::Coerce individual data frames (`shed_master`, shed_master1`, and 
# `shed_master2`) into one `shed_final` data set:

shed_final <- merge(x = shed_master, y = shed_master1, 
                    all = TRUE)

shed_final <- merge(x = shed_final, y = shed_master2, 
                    all = TRUE)

## For the models, I only want to see whether SHED respondents forecasted the 
## HPA up or down so recode H1 and H4 as follows:
shed_final$H4 <- recode(shed_final$H4, " '-1' = 2") ## refused becomes 2
shed_final$H4 <- recode(shed_final$H4, " '1' = 0") ## “Go down by more than 5 percent”, “go down by a lot”, “go down by 5 percent or less”, and “go down by a little” are coded as “0”
shed_final$H4 <- recode(shed_final$H4, " '2' = 0") ## “Go down by more than 5 percent”, “go down by a lot”, “go down by 5 percent or less”, and “go down by a little” are coded as “0”
#shed_final$H4 <- recode(shed_final$H4, " '3' = 3") ## 'Stay about the same' stays as 3 so no need to recode
shed_final$H4 <- recode(shed_final$H4, " '4' = 1") ## “Go up by 5 percent or less”, “go up by a little”, “go up by more than 5 percent”, and “go up by a lot” are coded as “1”
shed_final$H4 <- recode(shed_final$H4, " '5' = 1") ## “Go up by 5 percent or less”, “go up by a little”, “go up by more than 5 percent”, and “go up by a lot” are coded as “1”
shed_final$H4 <- recode(shed_final$H4, " '8' = 4") ## 'Don't know' becomes 4
#shed_final$H4 <- recode(shed_final$H4, " '' = NA") ## NA stays as NA so no need to recode

shed_final$H1 <- recode(shed_final$H1, " '-1' = 2") ## “Refused” is coded as “2”
shed_final$H1 <- recode(shed_final$H1, " '1' = 0") ## “Lower value”, “value is a lot lower”, and “value is a little lower” are coded as “0”
shed_final$H1 <- recode(shed_final$H1, " '1' = 0") ## “Lower value”, “value is a lot lower”, and “value is a little lower” are coded as “0”
shed_final$H1 <- recode(shed_final$H1, " 'Value has stayed the same' = 3") ## “Value has stayed the same” is coded as “3”
shed_final$H1 <- recode(shed_final$H1, " '3' = 1") ## o	 “Higher value”, “value is a lot higher”, and “value is a little higher” are coded as “1”
shed_final$H1 <- recode(shed_final$H1, " '3' = 1") ## o	 “Higher value”, “value is a lot higher”, and “value is a little higher” are coded as “1”
shed_final$H1 <- recode(shed_final$H1, " '8' = 4") ## don't know becomes 4
#shed_final$H1 <- recode(shed_final$H1, " '' = NA") ## NA stays as NA so no need to recode

shed_final.csv <- write.csv(shed_final, file = "shed_final.csv")
```

# Part 2: Core Logic Data

```{r}
corelogic_raw <- read.csv("/Users/StephanieLangeland/Desktop/Columbia/Data Analysis/Final Project/Core Logic/CoreLogic House Price Forecasts-2016q2_CCAR_new.csv")

# 1) In the SHED survey, states are aggregated into regons via the `PPREG9` variable, 
# which is coded as `state_region` in the `shed_final` dataset.

# Aggregate the states in the core logic data into the same categories by region as coded in the 
# `state_region` variables in the `shed_final` dataset to make the datasets comparable:

corelogic_raw$state_region <- corelogic_raw$State
summary(corelogic_raw$state_region)
```

Manually went through the dataset the determine each state:

```{r}
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'AR_OK' = 'AR' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'DC_VA_MD_WVMET' = 'DC' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'DE_MD_NJMET' = 'DE' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'GA_SC' = 'GA' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'IA_IL' = 'IA' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'IA_NE_SD' = 'IA' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'ID_WA' = 'ID' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'IL_WI' = 'IL' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'IN_MI' = 'IN' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'MA_CT' = 'MA' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'MD_WV' = 'MD' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'MD_DE' = 'MD' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'MO_KS' = 'MO' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'NC_SC' = 'NC' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'ND_MN' = 'ND' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'NE_IA' = 'NE' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'NJ_PAMET' = 'NJ' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'NY_NJMET' = 'NY' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'OH_PA' = 'OH' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'OR_WA' = 'OR' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'PA_NJ' = 'PA' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'RI_MA' = 'RI' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'SC_NC' = 'SC' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'TN_KY' = 'TN' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'TX_AR' = 'TX' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'UT_ID' = 'UT' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'VA_NC' = 'VA' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'VA_WV' = 'VA' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'MO_IL' = 'MS' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'TN_GA' = 'TN' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'OH_KY_IN' = 'OH' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'GA_AL' = 'GA' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'MN_WI' = 'MN' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'IN_KY' = 'IN' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'AR_MO' = 'AR' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'WV_KY_OH' = 'WV' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'TN_VA' = 'VA' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'WI_MN' = 'WI' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'KY_IN' = 'IN' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'TN_MS_AR' = 'TN' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'WV_OH' = 'WV' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'ALABAMA' = 'AL' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'ALASKA' = 'AK' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'ARIZONA' = 'AZ' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'ARKANSAS' = 'AR' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'CALIFORNIA' = 'CA' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'COLORADO' = 'CO' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'CONNECTICUT' = 'CT' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'DELAWARE' = 'DE' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'FLORIDA' = 'FL' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'GEORGIA' = 'GA' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'HAWAII' = 'HI' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'IDAHO' = 'ID' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'ILLINOIS' = 'IL' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'INDIANA' = 'IN' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'IOWA' = 'IA' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'KANSAS' = 'KS' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'KENTUCKY' = 'KY' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'LOUISIANA' = 'LA' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'MAINE' = 'ME' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'MARYLAND' = 'MD' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'MASSACHUSETTS' = 'MA' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'MICHIGAN' = 'MI' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'MINNESOTA' = 'MN' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'MISSISSIPPI' = 'MS' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'MISSOURI' = 'MO' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'MONTANA' = 'MT' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'NEBRASKA' = 'NE' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'NEVADA' = 'NV' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'NEW HAMPSHIRE' = 'NH' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'NEW JERSEY' = 'NJ' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'NEW MEXICO' = 'NM' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'NEW YORK' = 'NY' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'NORTH CAROLINA' = 'NC' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'NORTH DAKOTA' = 'ND' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'OHIO' = 'OH' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'OKLAHOMA' = 'OK' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'OREGON' = 'OR' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'PENNSYLVANIA' = 'PA' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'RHODE ISLAND' = 'RI' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'SOUTH CAROLINA' = 'SC' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'SOUTH DAKOTA' = 'SD' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'TENNESSEE' = 'TN' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'TEXAS' = 'TX' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'UTAH' = 'UT' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'VERMONT' = 'VT' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'VIRGINIA' = 'VA' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'WASHINGTON' = 'WA' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'WEST VIRGINIA' = 'WV' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'WISCONSIN' = 'WI' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'WYOMING' = 'WY' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'AL' = 'Alabama' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'AK' = 'Alaska' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'AZ' = 'Arizona' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'AR' = 'Arkansas' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'CA' = 'California' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'CO' = 'Colorado' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'CT' = 'Connecticut' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'DE' = 'Delaware' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'FL' = 'Florida' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'GA' = 'Georgia' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'HI' = 'Hawaii' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'ID' = 'Idaho' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'IL' = 'Illinois' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'IN' = 'Indiana' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'IA' = 'Iowa' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'KS' = 'Kansas' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'KY' = 'Kentucky' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'LA' = 'Louisiana' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'ME' = 'Maine' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'MD' = 'Maryland' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'MA' = 'Massachusetts' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'MI' = 'Michigan' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'MN' = 'Minnesota' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'MS' = 'Mississippi' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'MO' = 'Missouri' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'MT' = 'Montana' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'NE' = 'Nebraska' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'NV' = 'Nevada' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'NH' = 'New Hampshire' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'NJ' = 'New Jersey' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'NM' = 'New Mexico' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'NY' = 'New York' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'NC' = 'North Carolina' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'ND' = 'North Dakota' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'OH' = 'Ohio' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'OK' = 'Oklahoma' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'OR' = 'Oregon' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'PA' = 'Pennsylvania' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'RI' = 'Rhode Island' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'SC' = 'South Carolina' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'SD' = 'South Dakota' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'TN' = 'Tennessee' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'TX' = 'Texas' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'UT' = 'Utah' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'VT' = 'Vermont' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'VA' = 'Virginia' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'WA' = 'Washington' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'WV' = 'West Virginia' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'WI' = 'Wisconsin' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'WY' = 'Wyoming' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'DC' = 'District of Columbia' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'CAMET' = 'California' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'CORVALLIS' = 'Oregon' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'FLMET' = 'Florida' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'ILMET' = 'Illinois' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'INMET' = 'Indiana' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'MAMET' = 'Massachusetts' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'MDMET' = 'Maryland' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'MIMET' = 'Michigan' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'NHMET' = 'New Hampshire' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'NJMET' = 'New Jersey' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'NYMET' = 'New York' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'PAMET' = 'Pennsylvania' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'TXMET' = 'Texas' ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'WAMET' = 'Washington' ")
```

```{r}
summary(corelogic_raw$state_region)
corelogic_raw$state_full <- corelogic_raw$state_region
#assign each corelogic_raw$state_full to a region - create the varaible corelogic_raw$state_region:

corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'Connecticut' = 1 ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'Maine' = 1 ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'Massachusetts' = 1 ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'New Hampshire' = 1 ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'Rhode Island' = 1 ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'Vermont' = 1 ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'New Jersey' = 2 ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'New York' = 2 ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'Pennsylvania' = 2 ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'Indiana' = 3 ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'Illinois' = 3 ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'Michigan' = 3 ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'Ohio' = 3 ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'Wisconsin' = 3 ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'Iowa' = 4 ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'Kansas' = 4 ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'Minnesota' = 4 ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'Missouri' = 4 ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'Nebraska' = 4 ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'North Dakota' = 4 ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'South Dakota' = 4 ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'Delaware' = 5 ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'District of Columbia' = 5 ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'Florida' = 5 ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'Georgia' = 5 ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'Maryland' = 5 ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'North Carolina' = 5 ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'South Carolina' = 5 ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'Virginia' = 5 ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'West Virginia' = 5 ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'Alabama' = 6 ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'Kentucky' = 6 ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'Mississippi' = 6 ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'Tennessee' = 6 ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'Arkansas' = 7 ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'Louisiana' = 7 ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'Oklahoma' = 7 ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'Texas' = 7 ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'Arizona' = 8 ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'Colorado' = 8 ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'Idaho' = 8 ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'New Mexico' = 8 ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'Montana' = 8 ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'Utah' = 8 ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'Nevada' = 8 ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'Wyoming' = 8 ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'Alaska' = 9 ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'California' = 9 ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'Hawaii' = 9 ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'Oregon' = 9 ")
corelogic_raw$state_region <- recode(corelogic_raw$state_region, " 'Washington' = 9 ")

summary(corelogic_raw$state_region)

corelogic_final <- write.csv(corelogic_raw, file = "corelogic_final.csv") 
```




