---
title: "QMSS G5072 Homework 9"
author: Stephanie Langeland 
date: 2017-11-14
always_allow_html: yes
output: 
  html_document:
    keep_md: true
---


Web Scraping with Selectors
============================

In the exercise, we will extract one particular part of a wikipedia page - an 
info box - to get some structured information about current members of the U.S. 
senate.

Wikipedia does have an API. For the purpose of this exercise, we will pretend 
there is no API and simply read-in the HTML. 

Our example will rely on Mitch McConnell's Wikipedia page: https://en.wikipedia.org/wiki/Mitch_McConnell

#### 1. Get HTML

Get the content of the page into R.

```{r}
library(httr)

wiki_url <- "https://en.wikipedia.org/wiki/Mitch_McConnell"

wiki_import <- GET(wiki_url)
wiki_import

wiki_content <- content(wiki_import)
wiki_content
```


#### 2. Get the info box

On the right side of the page is a box of structured content, called an 
info box. Wikipedia has [many types of such info boxes](https://en.wikipedia.org/wiki/Wikipedia:List_of_infoboxes#Education) 
to provide content comparably for a group of articles of the same class (e.g. 
the Members of the U.S. senate, Fortune 500 companies, Crime Syndicates etc.)

a) Find the CSS class of the infobox.    

  * Using the Agenty tool, I found that the CSS class is `.vcard`.


b) Extract the part of the HTML document that contains the infobox using 
the CSS information.  

```{r}
library(rvest)

wiki_page <- read_html(
  wiki_url
)

wiki_page

vcard_nodes <- html_nodes(
  wiki_page,
  ".vcard"
)

vcard_nodes

vcard_text <- html_text(vcard_nodes)
vcard_text
```

#### 3. Make a data frame

a) Parse the infobox table HTML you obtained above into a data frame.  

```{r}
infobox_table <- html_node(x = wiki_page, 
                           xpath = '//*[@id="mw-content-text"]/div/table[1]')

infobox_table

infobox_table_df <- html_table(infobox_table)
#View(infobox_table_df)
```

b) Name the columns of the table you obtain _`key`_ and _`value`_. So, in the 
example for Mitch McConnell, "Deputy" would be the _key_, and the content 
information (i.e. the _value_)  is "John Cornyn".  

```{r}
colnames(infobox_table_df)[1] <- "key"
colnames(infobox_table_df)[2] <- "value"
```

c) Filter the data frame (and rename variables if necessary) to the "Full 
name", "Political Party", and "Children". Use this selection of variables for 
all subsequent questions.

```{r}
infobox_table_df[1, 1] <- "Full name"
infobox_table_df[1, 2] <- "Mitch McConnell"

library(dplyr)

sub_infobox_table_df <- infobox_table_df %>%
  filter(key == "Full name" |
           key == "Political party" |
           key == "Children") 

sub_infobox_table_df
```

You should now have the following data frame to work with:

#### 4. Make a function

a) Use the code above to make a function called `get_wiki_info` that uses a single 
input `url` (a Wikipedia URL) and outputs the data frame of the format above. There 
is no need to account for exceptions (e.g. no info box on the page; page does not 
exist etc.) - we will only use members of the U.S. Senate for this exercise.

```{r}
get_wiki_info <- function(x) {
  
  base_url <- "https://en.wikipedia.org/wiki/"
  
  senate_member <- x
  
  full_url <- paste0(
    base_url,
    senate_member
    )

  wiki_page1 <- read_html(
    full_url
    )
  
  vcard_nodes1 <- html_nodes(
    wiki_page1,
    ".vcard"
    )

  vcard_text1 <- html_text(vcard_nodes1)
  infobox_table1 <- html_node(x = wiki_page1, 
                              xpath = '//*[@id="mw-content-text"]/div/table[1]')
  
  infobox_table_df1 <- html_table(infobox_table1)
  
  infobox_table_df1[1, 1] <- "Full name"
  
  infobox_table_df1[1, 2] <- senate_member
  
  colnames(infobox_table_df1)[1] <- "key"
  
  colnames(infobox_table_df1)[2] <- "value"

  sub_infobox_table_df1 <- infobox_table_df1 %>%
    filter(key == "Full name" |
           key == "Political party" |
           key == "Children")
  
    
  if (nrow(sub_infobox_table_df1) == 2) {
    sub_infobox_table_df1[3, 1] <- "Children"
    sub_infobox_table_df1[3, 2] <- NA
  } else {
    sub_infobox_table_df1
  }

  sub_infobox_table_df1
}
```

b) Show how your function works on the following two URLs:  
  - https://en.wikipedia.org/wiki/Jeff_Flake  
  - https://en.wikipedia.org/wiki/Susan_Collins  
Depending on your previous function, you may receive an error message because 
Susan Collins has no entry for `Children`. Fix your function so that `NA` is 
recorded in such instances.

```{r}
get_wiki_info("Jeff_Flake")

get_wiki_info("Susan_Collins")
```
